---
title: "R from Scratch"
<<<<<<< HEAD
output: github_document
=======
output: html_document
>>>>>>> 290bf8a... developing report
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

How to get restarted with R after a fresh install. 

# Install R

Download and install latest version of R [here](https://cran.r-project.org/) 

Download and install Rstudio [preview version here](https://rstudio.com/products/rstudio/download/preview/) 

Install `devtools` 

```{r install-initial-packages, eval = FALSE}
install.packages("devtools")
devtools::install_github("r-lib/devtools")
```

# Personalize

Set theme to Tomorrow Night Bright

Turn off options to:

* restore `.Rdata` to workspace at startup
* save workspace to `.Rdata` on exit
    
Update `.Rprofile` based on advice from [here](http://kevinushey.github.io/blog/2015/02/02/rprofile-essentials/):

```{r edit-rprofile, eval = FALSE}
usethis::edit_r_profile()
```

# Update terminal

Follow general steps described [here](https://www.freecodecamp.org/news/how-to-configure-your-macos-terminal-with-zsh-like-a-pro-c0ab3f3c1156/)

Install command line interface tools for Xcode

```{zsh, eval = FALSE}
xcode-select —-install
```

Install homebrew

```{zsh, eval = FALSE}
/usr/bin/ruby -e "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/master/install)"
```

Install iTerm 

```{zsh iterm, eval = FALSE}
brew cask install iterm2
```

Install `Zsh` and `Oh My Zsh`

```{zsh, eval = FALSE}
brew install zsh
sh -c "$(curl -fsSL https://raw.githubusercontent.com/robbyrussell/oh-my-zsh/master/tools/install.sh)"
```

Change default terminal in Rstudio to `/bin/zsh`

<<<<<<< HEAD
# Git and GitHub

Follow the instructions from [happygitwithr.com](https://happygitwithr.com/). 

Installing Xcode command line tools above should install Git. 

Install a git client [GitKraken](https://www.gitkraken.com/download/mac)

Set up SSH keys for GitHub and protect with a passphrase. Do not use user password as the passphrase. 

```{zsh, eval = FALSE}
ssh-keygen -t rsa -b 4096 -C "USEFUL-COMMENT"
```

Check that SSH agent is running

```{zsh, eval = FALSE}
eval "$(ssh-agent -s)"
```

Copy `SSH-config` to `~/.ssh/config`

Provide SSH keys to [GitHub](https://github.com/settings/keys)

```{zsh, eval = FALSE}
pbcopy < ~/.ssh/id_rsa.pub
```

A few other details to make sure `git2r` is setup appropriately.

```{zsh, eval = FALSE}
brew install libssh2
brew install libgit2
```

```{r, eval = FALSE}
install_github("ropensci/git2r")
git2r::libgit2_features()
```





=======
# Git and Github

Follow the instructions from [happygitwithr.com](https://happygitwithr.com/). 

Installing Xcode command line tools above should install git. 

Install a git client [Gitkraken](https://www.gitkraken.com/download/mac)

Set up SSH keys for Github

```{zsh, eval = FALSE}
$ ssh-keygen -t rsa -b 4096 -C "USEFUL-COMMENT"
```

>>>>>>> 290bf8a... developing report

