---
title: "R Setup"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

How to get R up and running after a fresh install.

## Install R

Download and install latest version of R [here](https://cran.r-project.org/) 

Download and install Rstudio preview version [here](https://rstudio.com/products/rstudio/download/preview/) 

Install `devtools` and update from GitHub

```{r install-initial-packages, eval = FALSE}
install.packages("devtools")
devtools::install_github("r-lib/devtools")
```

## Personalize

Set theme to Tomorrow Night Bright

Turn off options to:

* restore `.Rdata` to workspace at startup
* save workspace to `.Rdata` on exit
    
Update `.Rprofile` based on advice from [here](http://kevinushey.github.io/blog/2015/02/02/rprofile-essentials/):

```{r edit-rprofile, eval = FALSE}
usethis::edit_r_profile()
```

## Update terminal

Follow general steps described [here](https://www.freecodecamp.org/news/how-to-configure-your-macos-terminal-with-zsh-like-a-pro-c0ab3f3c1156/)

Install command line interface tools for Xcode

```{zsh, eval = FALSE}
xcode-select —-install
```

Install homebrew

```{zsh, eval = FALSE}
/usr/bin/ruby -e "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/master/install)"
```

Install iTerm 

```{zsh iterm, eval = FALSE}
brew cask install iterm2
```

Install `Zsh` and `Oh My Zsh`

```{zsh, eval = FALSE}
brew install zsh
sh -c "$(curl -fsSL https://raw.githubusercontent.com/robbyrussell/oh-my-zsh/master/tools/install.sh)"
```

Change default terminal in Rstudio to `/bin/zsh`

## Git and GitHub

Follow the instructions from [happygitwithr.com](https://happygitwithr.com/). 

Installing Xcode command line tools above should install Git. 

Install the [GitKraken](https://www.gitkraken.com/download/mac) Git client

Set up Git config. Make sure email address matches what is in GitHub, especially if email privacy settings are activated.

```{r, eval = FALSE}
use_git_config(user.name = "William Oldham", 
               user.email = "44209581+wmoldham@users.noreply.github.com")
```

Vaccinate the global `.gitignore`

```{r, eval = FALSE}
git_vaccinate()
```

Set up the default editor for Git

```{zsh, eval = FALSE}
git config --global core.editor nano 
```

Set up SSH keys for GitHub and protect with a passphrase. Do not use user password as the passphrase. 

```{zsh, eval = FALSE}
ssh-keygen -t rsa -b 4096 -C "USEFUL-COMMENT"
```

Check that SSH agent is running

```{zsh, eval = FALSE}
eval "$(ssh-agent -s)"
```

Copy contents from `SSH-config` in this repo to `~/.ssh/config`

Add keys to SSH agent

```{zsh, eval = FALSE}
ssh-add -K ~/.ssh/id_rsa
```

Copy `SSH-config` to `~/.ssh/config`

Copy SSH key

```{zsh, eval = FALSE}
pbcopy < ~/.ssh/id_rsa.pub
```

Provide SSH keys to GitHub [here](https://github.com/settings/keys)

Set up a personal access token (PAT)

```{r, eval = FALSE}
browse_github_token()
```

Copy the token

```{r, eval = FALSE}
edit_r_environ()
```

Then add `GITHUB_PAT=` the token to `.Renviron`

Complete the `git2r` setup to use SSH keys

```{zsh, eval = FALSE}
brew install libssh2
brew install libgit2
```

```{r, eval = FALSE}
install_github("ropensci/git2r")
git2r::libgit2_features()
```

If this fails, consider problematic `Makevars` file (similar that used to compile `data.table` from source). 

Check to see how things are looking:

```{r, eval = FALSE}
git_sitrep()
```

